manuscript_outline

### 2025-07-11 docs/manuscript/paper.Rmd
format for journal

---
title: ""
output:  
  bookdown::pdf_document2:
    toc: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: apa.csl
bibliography: references.bib
---

@@

# A generalizable tool for predicting developmental phenology for wild poikilotherms.

Morgan M. Sparks^1,3^, Brian Z. Leavell^2^, Bryan M. Maitland^1^

^1^Rocky Mountain Research Station, U.S. Forest Service, Boise, Idaho, USA

^2^Division of Biological Sciences, Purdue University, West Lafayette, Indiana, USA

^3^Corresponding author, Morgan.Sparks\@usda.gov

keywords: hatchR, developmental phenology, local adaptation, reaction norm, R, Shiny

@@

@@

| Class | Order | Genus | Species | Study |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* | @angilletta2000 |
|  |  | *Podarcis* | *P. mural*is | @vandamme1992 |
|  | Testudines | *Mauremys* | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
|  | Coleoptera | *Colaphellus* | *C. bowringi* | @tang2017 |
|  |  |  | 18 species | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |
| Copepoda | Calanoida | 10 genera | 28 species | @forster2011 |
|  | Cyclopoida | *Limnoithona* | *L. tetraspina* |  |
|  |  | *Oithona* | *O. davisae* |  |
|  | Harpacticoida | *Microsetella* | *M. norvegica* |  |
|  |  | *Mesochra* | *M.lilljeborgi* |  |
|  | Poecilostomatoida | *Oncaea* | *O. venusta* |  |
| Cephalopoda | Octopoda | *Octopus* | *O. vulgaris* | @márquez2021 |
|  |  |  | *O. mimus* |  |
|  | Myopsida | *Loligo* | *L. vulgaris* |  |
|  |  |  | *L. reynaudii* |  |
|  | Oegopsida | *Illex* | *I. coindetii* |  |
|  |  |  | *I. illecebrosus* |  |
|  |  | *Todarodes* | *T.pacificus* |  |
|  |  | *Ommastrephes* | *O. bartramii* |  |
| Asteroidea | Valvatida | *Odontaster* | *O. meridionalis* | @hoegh-guldberg1995 |
|  |  |  | *O. validus* |  |
|  |  | *Asterina* | *A. miniata* |  |
|  |  | *Acanthaster* | *A. planci* |  |

@@

# Acknowledgements

We thank N. Karraker, D. Pilliod, M. Hayes, R.B. Bury, and B. Norman for their help in translating sites for the tailed frog example to locations that could be aligned with COMIDs. D. Horan helped organize GPS locations into COMIDs. The views expressed in this manuscript are those of the authors and do not necessarily represent the views or policies of USFS . Any mention of trade names, products, or services does not imply an endorsement by the U.S. government or USFS. USFS does not endorse any commercial products, services or enterprises.

>>>>

---
title: ""
output:  
  bookdown::pdf_document2:
    toc: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: methods-in-ecology-and-evolution.csl
bibliography: references.bib
---

@@

@@

keywords: developmental phenology, hatchR, local adaptation, R, reaction norm, Shiny

@@

| Class | Order | Genus | Species | Study |
|:---|:---|:---|:---|:---|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* | @angilletta2000 |
|  |  | *Podarcis* | *P. mural*is | @vandamme1992 |
|  | Testudines | *Mauremys* | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
|  | Coleoptera | *Colaphellus* | *C. bowringi* | @tang2017 |
|  |  |  | 18 species | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |
| Copepoda | Calanoida | 10 genera | 28 species | @forster2011 |
|  | Cyclopoida | *Limnoithona* | *L. tetraspina* |  |
|  |  | *Oithona* | *O. davisae* |  |
|  | Harpacticoida | *Microsetella* | *M. norvegica* |  |
|  |  | *Mesochra* | *M.lilljeborgi* |  |
|  | Poecilostomatoida | *Oncaea* | *O. venusta* |  |
| Cephalopoda | Octopoda | *Octopus* | *O. vulgaris* | @márquez2021 |
|  |  |  | *O. mimus* |  |
|  | Myopsida | *Loligo* | *L. vulgaris* |  |
|  |  |  | *L. reynaudii* |  |
|  | Oegopsida | *Illex* | *I. coindetii* |  |
|  |  |  | *I. illecebrosus* |  |
|  |  | *Todarodes* | *T.pacificus* |  |
|  |  | *Ommastrephes* | *O. bartramii* |  |
| Asteroidea | Valvatida | *Odontaster* | *O. meridionalis* | @hoegh-guldberg1995 |
|  |  |  | *O. validus* |  |
|  |  | *Asterina* | *A. miniata* |  |
|  |  | *Acanthaster* | *A. planci* |  |

@@
